Learning by Teaching a Robot:\\The Case of Handwriting

### 2016-01-13 main.tex
Remove mention of public/private schools -- Pierre's suggestion

\paragraph{Acceptance} When we started the project, the mere acceptance of the
robot in the educative and/or medical context of handwriting remediation was not
obvious. As expected, the attitude of practitioners toward the robot indeed
varies a lot at individual levels. The process that led us to select the schools
and clinics for the experiments is interesting in that regard. The very first
school we contacted was a local public school. The head teacher was positive
about the study, but did ask for official approval, which never happened. As we
learnt several months later, the request was still laying on the desk of a
regional education officer who happens to not be too keen on novel technologies.
Conversely, the three schools where we did conduct the first studies are all
private schools, generally open to novel learning methods. The teachers we met
during these experiments certainly had questions about the rationale and
end-purpose of the project, but were confident about its educative and social
value.

>>>>

\paragraph{Acceptance} When we started the project, the mere acceptance of the
robot in the educative and/or medical context of handwriting remediation was not
obvious. As expected, the attitude of practitioners toward the robot indeed
varies a lot at individual levels. The process that led us to select the schools
and clinics for the experiments is interesting in that regard.  The head teacher
of the very first school that we contacted was positive about the study, but he
could not obtain official approval from his hierarchy due to concerns with
technologies at school. The three schools where we did conduct the first studies
did not have such initial reservations. The teachers we met during these
experiments certainly had questions about the rationale and end-purpose of the
project, but were confident about its educative and social value.
